---
title: "W_UP_01"
author: "MarenaO"
date: "Spring 2022"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
boxplot(pushups~position,data=mydata)
```

Box that showed skill players was a bit higher than the box that showed the line players, which indicates that the skill players were doing more pushups than the line players.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(pushups~position,data=mydata)
```
Average number of pushups done by a line player is 17 and the average number of pushups done by a skill player is almost 50. SO, the skill players are doing almost 3 times as much pushups than the line players.  

## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(pushups~position,data=mydata)
```
There is a statistical difference between the amount of pushups between the skill group and the line group. This is because the value "zero" is not in the confidence interval in the difference. It would be somewhere between -44 and -20, meaning line players do less pushups than the skill players.

# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

I looked at the problem, imported the data. I noticed there was a problem with the plot, which was "boxplot," meaning I have to go back and fix my helper file next time I use it. The graphical data shows that the skill players were doing more pushups than the line players because the box of the skill players was a bit higher than the line players. I then ran a numerical test, which showed that the average number of pushups done by the skill players was about 3 times as much pushups than the line players. I then ran a T-test (statistical test), which showed that there was a statistical difference between the amount of pushups between the skill group and the line group, due to the value zero not being in the confidence interval, meaning I can reject the null hypothesis that there is no statistical difference.